---
title: "Life Expectancies"
author: "Dennis"
date: "May 12, 2018"
output:
  slidy_presentation: default
---

##Introduction

This presentation accompanies a Shiny app that can be used for comparing life expectancies between different countries. The Shiny app can be found [here](https://dennisdondergoor.shinyapps.io/jhu-ddp-shiny-and-pitch/).

###Assignment

This project is an assignment for the JHU/Coursera course **Developing Data Products**. 

###Github

The source code for this **Reproducible Pitch** presentation as well as for the **Shiny App** can be found in [this Github repo](https://github.com/DennisDondergoor/jhu-ddp-shiny-and-pitch).

## The Gapminder data

The data is taken from the **gapminder** dataset (which can be found in the corresponding R package). It contains an excerpt of the **Gapminder data** on life expectancy, GDP per capita, and population of 142 countries (1952 - 2007).

The **Gapminder data** can be found at [this website](https://www.gapminder.org/data/").
                    
## Summary statistics

Let's take a look at the data.

```{r, message = FALSE}
library(gapminder)
library(tidyverse)
data(gapminder)
head(gapminder)
unique(gapminder$year)
summary(gapminder)
```

## Life Expectancy

```{r, message = FALSE}
gapminder %>%
    filter(year == 1952) %>%
    summarise(min = min(lifeExp), max = max(lifeExp))
gapminder %>%
    filter(year == 2007) %>%
    summarise(min = min(lifeExp), max = max(lifeExp))
```

Life expectancies per country in 1952 vary from 28.8 to 72.7 years.

Life expectancies per country in 2007 vary from 39.6 to 82.6 years.
